Compositional equivalences based on Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-06-27 2016-Weak-FH-Bisim/WeakBisim.tex
modif

We let $\gamma$ range over lists of action terms and use $\dotcup$ as the union that appends lists of action terms: given two  lists of action terms  $\gamma\dotcup\gamma '$ concatenates teh two lists. The operation is lifted to indexed sets of lists where  $\set {\gamma_1}\dotcup \set {\gamma_2}$ is an indexed set of lists that at each index concatenates the listof  list of $\set{\gamma_1}$ and the one of $\set {\gamma_2}$ (where one of the two lists is empty when $j\not \in \dom(\set{\gamma_1})$). $[a]$ is a list with a single element.

@@

\begin{proof} 
($\Rightarrow$) First, we prove that Definition \ref{def-Weak-bisim} implies the definition above. In other words,
Suppose that $\Pred_{s,t}\in \mathcal{R}$ 
%and for any open transition $OT$ in $\mathcal{T}_1$:
% \begin{mathpar}
%     \openrule
%         {
%           \beta_j^{j\in J},\Pred_{OT},\Post_{OT}}
%         {s \OTarrow {\alpha} s'}
%\end{mathpar}
%there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
% \begin{mathpar}
%    \openrule
%         {
%           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
%         {t \OTWeakarrow {\alpha_x} t_x}
%\end{mathpar}
% such that  $\forall x, J_{x}=\{j\in J|\beta_j\neq\tau\}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
% and  \\
% $\Pred_{s,t} \land \Pred_{OT}\\
% \implies\!\!\!\displaystyle{\bigvee_{x\in X}}
%   \big(\forall j\in J_x. \vis{\beta_j}=\gamma_{jx}\Rightarrow \Pred_{OT_x}
%     \land \alpha\!=\!\alpha_x\land  
%     \Pred_{s',t_x}\subst{\Post_{OT}\shortotimes\Post_{OT_x}}\big)$\\
and  suppose that the following statement holds:
\begin{mathpar}
     \openrule
         {
           \gamma_j^{j\in J'},\Pred_{OT},\Post_{OT}}
         {s \OTWeakarrow {\alpha} s'} \in \WT_1

@@

For the sake of simplicity, we prove the rule in the  restricted case where $n$ and $m$ are equal to $1$, hence a single tau open transition will be considered on each side of the potentially visible one. The proof may be easily generalized to the multiple tau open transitions by using the same reasoning and (\WTTrois)~rule. Consider each open transition separately:
\begin{enumerate}
\item For the first open transition in $\mathcal{T}_1$:
\begin{mathpar}
%\inferrule{
 \openrule
    {
       \beta_{1j}^{j\in J_1'},\Pred_1,\Post_1   }
         {s_{10} \OTarrow {\tau} s_{11}}          
\end{mathpar}
by hypothesis we have $(s,t|\Pred_{s,t})\in\mathcal{R}$  and $s=s_{10}$. Thus, by  Definition \ref{def-Weak-bisim} we  can deduce there exist weak open transitions $\symb{WOT}_a^{a\in A} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j a}^{j\in J_{a}}, \Pred_{OT_a},\Post_{OT_a}}
         {u \OTWeakarrow {\alpha_{1 a}} u_a}
\end{mathpar}
 such that  $\forall a, J_{a}=\{j\in J_1'|\beta_{1j}\neq\tau\}, u=t,  (s_{11},u_a|\Pred_{s_{11},u_a})\in \mathcal{R}$ and \\
 $\Pred_{s,t} \land \Pred_1\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}}
  \!\! \left( \forall j\in J_a.\vis{\beta_{1j}}=\gamma_{ja}  \Rightarrow \Pred_{OT_a}
     \land \alpha_{1 a}\!=\!\tau \land  
     \Pred_{s_{11},u_a}\subst{\Post_1\uplus\Post_{OT_a}}\right)$

 Note that, because $\AlgE\cap\AlgA=\emptyset$  (actions and expressions are disjoint) and $\alpha_{1 a}\!=\!\tau$ we have 
directly ($\alpha_{1 a}$ cannot be a variable, and cannot contain expressions/variables because $\tau$ has no parameter):
\begin{mathpar}
    \openrule
         {
           \gamma_{j a}^{j\in J_{a}}, \Pred_{OT_a},\Post_{OT_a}}
         {u \OTWeakarrow {\tau} u_a}
\end{mathpar}
%and\\
%$\Pred_{s,t} \land \Pred_1\\
%\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}}
%  \!\! \left( \forall j\in J_a.\vis{\beta_{1j}}=\gamma_{ja}  \Rightarrow \Pred_{OT_a}
%     \land    \Pred_{s_{11},u_a}\subst{\Post_1\uplus\Post_{OT_a}}\right)$
%

\item Concerning the middle open transition in $\mathcal{T}_1$:
 \begin{mathpar}
     \openrule
         {
           \beta_{2j}^{j \in J_2'},\Pred_2,\Post_2 }
         {s_{20} \OTarrow {\alpha'} s_{21}} 
\end{mathpar}
we have  $(s_{11},u_a|\Pred_{s_{11},u_a})\in \mathcal{R}$  and $s_{11}=s_{20}$. Again 
 by Definition \ref{def-Weak-bisim} we can deduce there exist weak open transitions $\symb{WOT}_{b}^{b\in B} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j b}^{j\in J_{b}}, \Pred_{OT_{b}},\Post_{OT_{b}}}
         {u_a \OTWeakarrow {\alpha_{2 b}} v_{b}}
\end{mathpar}
 such that  $\forall b, J_{b}=\{j\in J_2'|\beta_{2j}\neq\tau\}, 
(s_{21},v_{b}|\Pred_{s_{21},v_{b}})\in \mathcal{R}$; \\
 $\Pred_{s_{11},u_a} \land \Pred_2\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{b\in B}}
 \!\!  \left( \forall j\in J_{b}. \vis{\beta_{2j}}\!=\!\gamma_{jb}\Rightarrow \Pred_{OT_{b}}\!\land \alpha'\!=\!\alpha_{2 b} \land  
     \Pred_{s_{21},v_{b}}\subst{\Post_2\uplus\Post_{OT_{b}}}\right)$

\item Similarly to the case 1, we consider the third  open transition in $\mathcal{T}_1$:
     \begin{mathpar}
%\inferrule{
 \openrule
    {
       \beta_{3j}^{j \in J_3'},\Pred_3,\Post_3   }
         {s_{30} \OTarrow {\tau} s_{31}} \in \mathcal{T}          
\end{mathpar}
From previous case, we have $(s_{21},v_{b}|\Pred_{s_{21},v_{b}})\in \mathcal{R}$, and we have $s_{21}=s_{30}$. Then, by
 Definition \ref{def-Weak-bisim} there exist weak open transition $\symb{WOT}_{a}^{c\in C} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{jc}^{j\in J_{c}}, \Pred_{OT_{c}},\Post_{OT_{c}}}
         {v_{b} \OTWeakarrow {\tau} w_{c}}
\end{mathpar}
 such that  $\forall c, J_{c}= \{j\in J_3'|\beta_{3j}\neq\tau\}, 
(s_{31},w_{c}|\Pred_{s_{31},w_{c}})\in \mathcal{R}$ and \\
 $\Pred_{s_{21},v_{b}} \land \Pred_3\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{c\in C}}
   \!\left( \forall j\in J_{c}. \vis{\beta_{3j}}\!=\!\gamma_{jc} \! \Rightarrow\! \Pred_{OT_{c}}\!
     \land\!  
     \Pred_{s_{31},w_{c}}\subst{\Post_3\uplus\Post_{OT_{c}}}\right)$

@@

\set{\gamma'}=\gamma_{j a}^{j\in J_{a}} \dotcup \gamma_{j b}^{j\in J_{b}} \subst{\Post_{OT_a}} \dotcup\gamma_{jc}^{j\in J_{c}} \subst{\Post_{OT_{ b}}\shortotimes\Post_{OT_a}}\\

@@

We now need to prove that the following statement holds:\\

@@

     Let's start with the hypothesis \TODO{ je vois pas ce que u=t apporte -- Ludo} and consider  $u=t$   we have:\\

@@

Moreover, we have the following  statement:\\

@@

With the conjunction of the predicate $\Pred_2\subst{\Post_1}$ on both sides of the implication, we get:\\  

@@

Note that  on the right side of the implication we added  the substitution  of $\Post_{OT_x}$ without affecting the validity of the statement, because  the domain  of the substitution $\Post_{OT_x}$ is disjoint from the others. Hence a little rewriting gives:\\

@@

    \forall j\in J_{b}. \vis{\beta_{2j}}\!=\!\gamma_{jb}  \Rightarrow \Pred_{OT_{b}}\land \alpha'\!=\!\alpha_{2 b}\! \land \Pred_{s_{21},v_{b}}\subst{\Post_2\uplus\Post_{OT_{b}}})\subst{\Post_1\uplus\Post_{OT_a}})$\\
This can be rewritten into:\\

@@

(\forall j\in J_a. \vis{\beta_{1j}}\!\!=\!\gamma_{ja} \land  \forall j \in J_{b}. (\vis{\beta_{2j}}\!=\!\gamma_{jb})\subst{\Post_1\uplus\Post_{OT_a}}   \Rightarrow\Pred_{OT_a} \land  \Pred_{OT_{b}} \subst{\Post_1\uplus\Post_{OT_a}} \land  (\alpha'\!=\!\alpha_{2 b}) \subst{\Post_1\uplus\Post_{OT_a}} \land \\ \Pred_{s_{21},v_{b}}\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{b}}\shortotimes \Post_{OT_a}})$\\ 
Since $Post_1$  does not act on $\gamma_{jb}$, nor on $ \Pred_{OT_{b}}$ and $  \alpha_{2}$. As well $\Post_{OT_a}$  does not act on $\alpha'$, nor on  $\beta_{2j}$ the formula can be simplified as follows:\\

@@

(\forall j\in J_a. \vis{\beta_{1j}}\!=\!\gamma_{ja} \land  \forall j \in J_{b}. \vis{\beta_{2j}}\subst{\Post_1}=\gamma_{jb} \subst{\Post_{OT_a}}  \Rightarrow\Pred_{OT_a} \land  \Pred_{OT_{b}} \subst{\Post_{OT_a}} \land \alpha'\subst{\Post_1}=\alpha_{2 b} \subst{\Post_{OT_a}} \land \Pred_{s_{21},v_b}\\\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{b}}\shortotimes \Post_{OT_a}})$\\ 

@@

\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}} \displaystyle{\bigvee_{b\in B}} 
(\forall j\in J_a.\vis{\beta^1_j}\!=\!\gamma_{ja} \land  \forall j \in J_{b}. \vis{\beta_{2j}}\subst{\Post_1}\!=\!\gamma_{jb} \subst{\Post_{OT_a}}\Rightarrow \Pred_{OT_a}\land\Pred_{OT_{b}}\subst{\Post_{OT_a}} \land  \alpha'\subst{\Post_1}= \alpha_{2 b} \subst{\Post_{OT_a}} \land (\Pred_{s_{21},v_b} \land  \Pred_3)\\ \subst{\Post_2\shortotimes \Post_1\uplus \Post_{OT_{b}}\shortotimes\Post_{OT_a}})$\\ 
Again note that because of the domain  of the substitution is independent from some predicates and expressions, we removed $\Post_1$ and  we  added the term $\Post_{OT_{b}}\shortotimes\,\Post_{OT_a}$ in the substitution of the right side of the implication.\\

@@

  \Pred_{OT_{c}}\subst{\Post_{OT_{b}}\shortotimes\Post_{OT_a}}}_{\Pred} \land  \underbrace{\alpha'\subst{\Post_1}}_{\alpha}=\underbrace{\alpha_{2 b} \subst{\Post_{OT_a}}}_{\alpha''} \land\\ \Pred_{s_{31},w_{c}}  \subst{\underbrace{\Post_3\shortotimes\Post_2\shortotimes\Post_1}_{\Post_{OT}}\uplus \underbrace{\Post_{OT_{c}}\shortotimes \Post_{OT_{b}}\shortotimes\Post_{OT_a}}_{\Post}})$\\
The three for all statements (on $J_a$, $J_b$, and $J_c$) can be concatenated using $\dotcup$, the list union lifted to indexed sets (if $\gamma=\gamma'$ and $\gamma''=\gamma'''$ then $\gamma\dotcup\gamma''=\gamma'\dotcup\gamma'''$).\\

@@

\TODO{we miss the other direction no?}

>>>>

We let $\gamma$ range over lists of action terms and use $\dotcup$ as the union that appends lists of action terms \TODO{write this properly}. $[a]$ is a list with a single element.

@@

\begin{proof} 
($\Rightarrow$) Firstly, we prove that Definition \ref{def-Weak-bisim} implies definition above.\\
Suppose that $\Pred_{s,t}\in \mathcal{R}$ 
%and for any open transition $OT$ in $\mathcal{T}_1$:
% \begin{mathpar}
%     \openrule
%         {
%           \beta_j^{j\in J},\Pred_{OT},\Post_{OT}}
%         {s \OTarrow {\alpha} s'}
%\end{mathpar}
%there exist weak open transitions $\symb{WOT}_x^{x\in X} \subseteq \WT_2$:
% \begin{mathpar}
%    \openrule
%         {
%           \gamma_{j x}^{j\in J_{x}}, \Pred_{OT_x},\Post_{OT_x}}
%         {t \OTWeakarrow {\alpha_x} t_x}
%\end{mathpar}
% such that  $\forall x, J_{x}=\{j\in J|\beta_j\neq\tau\}, (s',t_x|\Pred_{s',t_x})\in \mathcal{R}$; 
% and  \\
% $\Pred_{s,t} \land \Pred_{OT}\\
% \implies\!\!\!\displaystyle{\bigvee_{x\in X}}
%   \big(\forall j\in J_x. \vis{\beta_j}=\gamma_{jx}\Rightarrow \Pred_{OT_x}
%     \land \alpha\!=\!\alpha_x\land  
%     \Pred_{s',t_x}\subst{\Post_{OT}\shortotimes\Post_{OT_x}}\big)$\\
and  suppose that the following statement holds:
\begin{mathpar}
     \openrule
         {
           \gamma_j^{j\in J'},\Pred_{OT},\Post_{OT}}
         {s \OTWeakarrow {\alpha} s'} \in \WT_1

@@

For the sake of simplicity, we prove the rule in the  restricted case where $n$ and $m$ to be equal to $1$, hence a single tau open transition will be considered on each side of the potentially visible one. The proof may be easily generalized to the multiple tau open transitions by using the same reasoning and (\WTTrois)~rule. Consider each open transition separately:
\begin{enumerate}
\item For the first open transition in $\mathcal{T}_1$:
\begin{mathpar}
%\inferrule{
 \openrule
    {
       \beta_{1j}^{j\in J_1'},\Pred_1,\Post_1   }
         {s_{10} \OTarrow {\tau} s_{11}}          
\end{mathpar}
by hypothesis we have $(s,t|\Pred_{s,t})\in\mathcal{R}$  and $s=s_{10}$. Thus, by  Definition \ref{def-Weak-bisim} we  can deduce there exist weak open transitions $\symb{WOT}_a^{a\in A} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{j a}^{j\in J_{a}}, \Pred_{OT_a},\Post_{OT_a}}
         {u \OTWeakarrow {\alpha_1} u_a}
\end{mathpar}
 such that  $\forall a, J_{a}=\{j\in J_1'|\beta_{1j}\neq\tau\}, u=t,  (s_{11},t_a|\Pred_{s_{11},u_a})\in \mathcal{R}$ and \\
 $\Pred_{s,t} \land \Pred_1\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}}
  \!\! \left( \forall j\in J_a.\vis{\beta_{1j}}=\gamma_{ja}  \Rightarrow \Pred_{OT_a}
     \land \alpha_1\!=\!\tau \land  
     \Pred_{s_{11},u_a}\subst{\Post_1\uplus\Post_{OT_a}}\right)$

Note that, because $\AlgE\cap\AlgA=\emptyset$  (actions and expressions are disjoint) and $\alpha_x\!=\!\tau$ we have 
directly ($\alpha_a$ cannot be a variable, and cannot contain expressions/variables because $\tau$ has no parameter):
\begin{mathpar}
    \openrule
         {
           \gamma_{j a}^{j\in J_{a}}, \Pred_{OT_a},\Post_{OT_a}}
         {u \OTWeakarrow {\tau} u_a}
\end{mathpar}
and//
$\Pred_{s,t} \land \Pred_1\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{a\in A}}
  \!\! \left( \forall j\in J_a.\vis{\beta_{1j}}=\gamma_{ja}  \Rightarrow \Pred_{OT_a}
     \land    \Pred_{s_{11},u_a}\subst{\Post_1\uplus\Post_{OT_a}}\right)$

\item Concerning the middle open transition in $\mathcal{T}_1$:
 \begin{mathpar}
     \openrule
         {
           \beta_{2j}^{j \in J_2'},\Pred_2,\Post_2 }
         {s_{20} \OTarrow {\alpha'} s_{21}} 
\end{mathpar}
we have  $(s_{11},u_a|\Pred_{s_{11},u_a})\in \mathcal{R}$  and $s_{11}=s_{20}$. Again 
 by Definition \ref{def-Weak-bisim} we can deduce there exist weak open transitions $\symb{WOT}_{b}^{b\in B} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{b}^{j\in J_{b}}, \Pred_{OT_{b}},\Post_{OT_{b}}}
         {u_a \OTWeakarrow {\alpha_{2}} v_{b}}
\end{mathpar}
 such that  $\forall b, J_{b}=\{j\in J_2'|\beta_{2j}\neq\tau\}, 
(s_{21},v_{y}|\Pred_{s_{21},v_{y}})\in \mathcal{R}$; \\
 $\Pred_{s_{11},u_a} \land \Pred_2\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{b\in B}}
 \!\!  \left( \forall j\in J_{b}. \vis{\beta_{2j}}\!=\!\gamma_{jb}\Rightarrow \Pred_{OT_{b}}\!\land \alpha'\!=\!\alpha_{2} \land  
     \Pred_{s_{21},v_{b}}\subst{\Post_2\uplus\Post_{OT_{b}}}\right)$

\item Similarly to the case 1,  the third  open transition in $\mathcal{T}_1$:
     \begin{mathpar}
%\inferrule{
 \openrule
    {
       \beta_{3j}^{j \in J_3'},\Pred_3,\Post_3   }
         {s_{30} \OTarrow {\tau} s_{31}} \in \mathcal{T}          
\end{mathpar}
From previous case, we have $(s_{21},v_{b}|\Pred_{s_{21},v_{b}})\in \mathcal{R}$, and we have $s_{21}=s_{30}$. Then, by
 Definition \ref{def-Weak-bisim} there exist weak open transition $\symb{WOT}_{a}^{c\in C} \subseteq \WT_2$:
 \begin{mathpar}
    \openrule
         {
           \gamma_{jc}^{j\in J_{c}}, \Pred_{OT_{c}},\Post_{OT_{c}}}
         {v_{b} \OTWeakarrow {\tau} w_{c}}
\end{mathpar}
 such that  $\forall c, J_{c}= \{j\in J_3'|\beta_{3j}\neq\tau\}, 
(s_{31},w_{c}|\Pred_{s_{31},w_{c}})\in \mathcal{R}$ and \\
 $\Pred_{s_{21},v_{b}} \land \Pred_3\\
\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{c\in C}}
   \!\left( \forall j\in J_{c}. \vis{\beta_{3j}}\!=\!\gamma_{jc} \! \Rightarrow\! \Pred_{OT_{c}}\!
     \land\!  
     \Pred_{s_{31},w_{c}}\subst{\Post_3\uplus\Post_{OT_{c}}}\right)$

@@

\set{\gamma'}=\gamma_{j a}^{j\in J_{a}} \dotcup \gamma_{jb}^{j\in J_{b}} \subst{\Post_{OT_a}} \dotcup\gamma_{jc}^{j\in J_{c}} \subst{\Post_{OT_{ b}}\shortotimes\Post_{OT_a}}\\

@@

So need to prove that the following statement holds:\\

@@

     Let's start with the hypothesis and consider  $u=t$   we have:\\

@@

Moreover, we have the following the statement:\\

@@

The conjunction of the predicate $\Pred_2\subst{\Post_1}$ with the both sides of the implication, we get:\\  

@@

Note that  on the right side of the implication we added  the substitution  of $\Post_{OT_x}$ without affecting the validity of the statement, because of the domain independence of the substitution. Hence a little rewriting gives:\\

@@

    \forall j\in J_{b}. \vis{\beta_{2j}}\!=\!\gamma_{jb}  \Rightarrow \Pred_{OT_{b}}\land \alpha'\!=\!\alpha_2\! \land \Pred_{s_{21},v_{b}}\subst{\Post_2\uplus\Post_{OT_{b}}})\subst{\Post_1\uplus\Post_{OT_a}})$\\
Furthermore, the rewriting of the formula gives:\\

@@

(\forall j\in J_a. \vis{\beta_{1j}}\!\!=\!\gamma_{ja} \land  \forall j \in J_{b}. (\vis{\beta_{2j}}\!=\!\gamma_{jb})\subst{\Post_1\uplus\Post_{OT_a}}   \Rightarrow\Pred_{OT_a} \land  \Pred_{OT_{b}} \subst{\Post_1\uplus\Post_{OT_a}} \land  (\alpha'\!=\!\alpha_{2}) \subst{\Post_1\uplus\Post_{OT_a}} \land \\ \Pred_{s_{21},v_{b}}\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{b}}\shortotimes \Post_{OT_a}})$\\ 
Since $Post_1$  does not act on $\gamma_{jb}$, nor on $ \Pred_{OT_{b}}$ and $  \alpha_{2}$, as well $\Post_{OT_a}$  does not act on $\alpha'$, nor on  $\beta_{2j}$ the formula can be simplified as follows:\\

@@

(\forall j\in J_a. \vis{\beta_{1j}}\!=\!\gamma_{ja} \land  \forall j \in J_{b}. \vis{\beta_{2j}}\subst{\Post_1}=\gamma_{jb} \subst{\Post_{OT_a}}  \Rightarrow\Pred_{OT_a} \land  \Pred_{OT_{b}} \subst{\Post_{OT_a}} \land \alpha'\subst{\Post_1}=\alpha_{2} \subst{\Post_{OT_a}} \land \Pred_{s_{21},v_b}\\\subst{\Post_2\shortotimes\Post_1\uplus \Post_{OT_{b}}\shortotimes \Post_{OT_a}})$\\ 

@@

\hspace{1cm} \implies\!\!\! \displaystyle{\bigvee_{x\in X}} \displaystyle{\bigvee_{y\in Y}} 
(\forall j\in J_a.\vis{\beta^1_j}\!=\!\gamma_{ja} \land  \forall j \in J_{b}. \vis{\beta_{2j}}\subst{\Post_1}\!=\!\gamma_{jb} \subst{\Post_{OT_a}}\Rightarrow \Pred_{OT_a}\land\Pred_{OT_{b}}\subst{\Post_{OT_a}} \land  \alpha'\subst{\Post_1}= \alpha_{2} \subst{\Post_{OT_a}} \land (\Pred_{s_{21},v_b} \land  \Pred_3)\\ \subst{\Post_2\shortotimes \Post_1\uplus \Post_{OT_{b}}\shortotimes\Post_{OT_a}})$\\ 
Again note that because of the domain independence of the substitution, we removed $\Post_1$ and  we  added the term $\Post_{OT_{b}}\shortotimes\,\Post_{OT_a}$ in the substitution of the right side of the implication.\\

@@

  \Pred_{OT_{c}}\subst{\Post_{OT_{b}}\shortotimes\Post_{OT_a}}}_{\Pred} \land  \underbrace{\alpha'\subst{\Post_1}}_{\alpha}=\underbrace{\alpha_{2} \subst{\Post_{OT_a}}}_{\alpha''} \land\\ \Pred_{s_{31},w_{c}}  \subst{\underbrace{\Post_3\shortotimes\Post_2\shortotimes\Post_1}_{\Post_{OT}}\uplus \underbrace{\Post_{OT_{c}}\shortotimes \Post_{OT_{b}}\shortotimes\Post_{OT_a}}_{\Post}})$\\
 \TODO{Comment passer a ca?}\\

@@

 This is exactly what we needed to prove. \qed
